Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-07-12 paperDraft.tex
some on model selection and added plot

\subsubsection{Weibull Model}
The exponential model is by far the most common parametric distribution used in
reliability modeling because of its desirable math mathematical properties and
simple interpretations.   Dispite its common uses the assumption of a constant
failure rate over time is rarely justifiable.  It has been well documented
(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
the issues that can arise when this assumption is violated.  We will now
consider the same hierarchical model structure while using the Weibull
distribution for each miles between failure observation.
\begin{align}
y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\kappa_{i}$.  The exponential is a special
case of the Weibull, when $\kappa = 1$.
\\
Talk about how to index the shape parameter and what it means

\subsubsection{JLTV Model Fitting}
So far we have discussed a number of different models and the assumptions that
accompany them.  Now looking at the JLTV dataset we will run a few diagnostics to
decide what model we will use for inference and future test planning.
\\
Models: \\
Exponential and Weibull with no hierarchy \\
Exponential and Weibull full hierarchy \\
Exponential and Weibull full hierarchy \\
Weibull with multipule shape vs. one shape \\
\\
DIC \\
posterior predictive checks \\
QQ Plots \\
Shape Parameter Plot \\

>>>>

\subsubsection{Weibull Model}
The exponential model is by far the most common parametric distribution used in
reliability modeling because of its desirable math mathematical properties and
simple interpretations.   Dispite its common uses the assumption of a constant
failure rate over time is rarely justifiable.  It has been well documented
(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
the issues that can arise when this assumption is violated.  We will now
consider the same hierarchical model structure while using the Weibull
distribution for each miles between failure observation.
\begin{align}
y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\kappa_{i}$.  The exponential is a special
case of the Weibull, when $\kappa = 1$.
\\
***Talk about how to index the shape parameter and what it means

\subsubsection{JLTV Model Selection}
So far we have discussed a number of different models and the assumptions that
accompany them.  We will now discuss the process of model selection.  The
decision of which model to use can have a drastic impact on reliability
assessment and future test planning.  We will use the JLTV dataset to
demonstrate the process.

The first model selection question we will explore is the parametric form,
exponential versus Weibull.  In statistical modeling we often face the
trade-off between fit and interpretability, and this situation is no different.
Because the Weibull is a more flexible model, it will always, in a sense, fit the
data better, but this comes at a price.  The exponential's convenient form
makes both computation and interpretation straight forward.  When the Weibull's
shape parameter is introduced this advantage is lost.  Thus, when the overall
fit is close to the same between the exponential and the Weibull we will
defualt to using the exponential.

The first check we used to decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the
shape parameters and determine if one is a reasonable value.  Looking at the
plot below from the JLTV data, we see that for the 26 components it appears
that the value of one falls in the extreme tails of the distributions.  This is
our first clue that the exponential model will not be a good fit to this data.

\includegraphics[width=6cm, height=5cm]{betaPostPlot}

Not suprising, the exponential model assumes constant failure rate.  shapes less
than 1 means wears out over time.  shapes more than 1 either fail early or last
long time.

Look at the DIC values for different indexings

Last check, we do post predictive checks to see if we get reasonable values.
